\section{Results}

\subsection{Therapy Benchmarks}

Existing therapies define the evidence bar. HSCT, lentiviral gene therapy, and
editing-enabled fetal hemoglobin reactivation establish that transfusion
independence is biologically achievable in selected patients. Luspatercept and
mitapivat define disease-modifying benchmarks for transfusion burden,
hemoglobin response, erythroid maturation, and red-cell metabolism
\cite{cappellini2020luspatercept,taher2025energize,fda2025aqvesme}. The China
\texttt{CS-101} phase 1 report is now the strongest Asia editing benchmark in
this map because it describes autologous base-edited CD34+ cells targeting the
BCL11A binding motif in the \texttt{HBG1/HBG2} promoters, with all 5 treated
patients stopping red-cell transfusions in the abstracted follow-up
\cite{lai2026cs101BaseEditing,clinicaltrials2026cs101}. The new
\texttt{NCT07489196} phase 2 registry record strengthens this from a phase 1
signal into an active development benchmark with safety, survival, engraftment,
12-month transfusion-independence, editing-efficiency, HbF, and total
hemoglobin endpoints \cite{clinicaltrials2026cs101Phase2}. A separate
China-registered \texttt{VGB-Ex01} trial remains a close mechanism benchmark
because its registry description links \texttt{HBG1/2} promoter editing to HbF
induction, reduced uncompounded alpha-globin burden, improved red-cell
survival, reduced hemolysis, and lower transfusion need
\cite{clinicaltrials2026vgbEx01}. A China pharmacologic record,
\texttt{NCT07338344}, is the closest current non-editing comparator because it
tests luspatercept plus low-dose thalidomide with transfusion-burden,
HbF/gamma-globin, hemolysis, iron, and safety endpoints
\cite{clinicaltrials2026luspaterceptThalidomide}. A second China record,
\texttt{NCT06302491}, adds an oral non-editing benchmark for safety,
hemoglobin, red-cell indices, transfusion-load, and iron-marker endpoints, but
the compact source pass does not show HbF/gamma-globin, hemolysis,
alpha-globin, autophagy, or posted results \cite{clinicaltrials2026and017}.

\input{tables/therapy-benchmark}

\subsection{Mechanism Map}

The central disease logic is not only low beta-globin. Beta-globin deficiency
creates globin-chain imbalance, ineffective erythropoiesis, chronic transfusion
need, iron loading, and organ-risk complexity. A credible affordable candidate
must therefore declare which intervention point it targets and which safety
readouts can falsify it.

\input{figures/mechanism-map}

\subsection{Candidate Gates}

Current candidates are not treatment recommendations. They are screened against
mechanism, evidence, identity, safety, assay feasibility, affordability, and
clinician-review gates. New candidate claims must also declare how they differ
from the closest editing and non-editing proximity benchmarks. This keeps
Quran-linked, natural-product, and repurposing ideas from being promoted just
because they are interesting.

\input{tables/candidate-gate}

\subsection{No-Lab Clinical Packet}

The most useful immediate no-lab output is a de-identified clinical packet for a
hematologist. Incomplete subtype, genotype, transfusion, immune, iron, organ,
and access data currently block patient-specific interpretation. The latest
case-001 molecular gate turns the \texttt{phenotype\_only} label into an
explicit record sequence: historical HPLC transfusion proximity,
\texttt{HBB}, \texttt{HBA1/HBA2}, HPFH/delta-beta or \texttt{HBG} modifier
context, and family fallback records when patient records are unavailable.
The advanced-therapy referral gate adds a stricter label,
\texttt{advanced\_therapy\_referral\_packet\_missing}, because HSCT,
gene addition, gene editing, disease-modifying drugs, and trials require a
specialist-readable packet before eligibility, ineligibility, suitability, or
access status can be discussed
\cite{pinto2025tifHsct,locatelli2025tifGeneManipulation,fda2022zynteglo,fda2026casgevy,nice2024exacel}.

\input{tables/no-lab-packet}

\subsection{Public-Repository Guardrails}

The repository now includes executable checks for public-facing hygiene:
scaffold completeness, English-only repo-authored prose, public privacy and
secret-pattern screening, and dependency-free checker self-tests. These controls
do not provide legal de-identification certification, but they reduce the chance
that raw case files, local paths, identifiers, generated caches, or mixed-language
repo-authored text enter the public record.

\subsection{Referral Snapshot}

The 2026-04-27 ClinicalTrials.gov refresh found no active Indonesia-located
thalassemia records in the local snapshot, while regional and global searches
returned active or active-not-recruiting signals. China was the highest-yield
regional query in this pass and produced the closest current editing benchmark.
These records are referral context only. They do not establish eligibility for
any patient.

\input{tables/referral-snapshot}
