\section{Ethics, Privacy, and Availability Statements}

\subsection{Medical Boundary}

This manuscript and repository are not medical advice. They do not recommend
diagnosis, dosing, transfusion changes, chelation changes, immune therapy,
supplement use, trial enrollment, or travel for treatment. Clinical decisions
belong to licensed clinicians.

\subsection{Privacy}

Patient-facing work is de-identified. The repository must not contain names,
exact addresses, hospital record numbers, phone numbers, identity numbers, face
photos, exact birth dates, raw clinical PDFs, scans, local source paths, or
patient-specific treatment instructions. This is a public-repo guardrail, not a
legal de-identification certification.

\subsection{AI Use}

AI assistance was used for source retrieval planning, summarization, document
drafting, cross-linking, and code generation. Nakafa Lab remains responsible for
the manuscript, source trail, and claim boundaries.

\subsection{Data and Code Availability}

The public repository contains source snapshots, research notes, LaTeX source,
templates, and Python utilities at \url{https://github.com/nakafaai/nakafa.lab}.
Generated local caches and build outputs are excluded from the public repo.
Repository checks cover scaffold completeness, English-only authored content,
public privacy screening, and checker self-tests.

\subsection{Funding and Competing Interests}

No external funding or competing interests are declared in this draft.

\section{Conclusion}

Nakafa Lab has not found a cure. The current contribution is a public,
source-backed research system that narrows the next credible path: specialist
case-packet review, benchmarked therapy/referral mapping, and a dual-readout
assay program for affordable HbF and globin-balance candidates.
