\documentclass[11pt]{article}

\usepackage[margin=0.72in]{geometry}
\usepackage{array}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{xurl}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!60!black,
  urlcolor=blue!60!black
}

\newcolumntype{Y}{>{\raggedright\arraybackslash\hspace{0pt}}X}
\setlist[itemize]{leftmargin=*, itemsep=2pt, topsep=3pt}
\setlist[enumerate]{leftmargin=*, itemsep=2pt, topsep=3pt}
\emergencystretch=3em

\title{Case-001 Branch-Review Doctor Handoff}
\author{Nakafa Lab}
\date{Prepared 2026-07-02}

\begin{document}

\maketitle

\noindent\textbf{Status:} de-identified clinician conversation aid, not
medical advice. No raw records, identifiers, exact dates, local file paths,
doctor identity, hospital identity, contact details, or patient-specific
treatment instructions are included.

\section*{Why We Are Asking}

The family is not asking for treatment changes from this document. The request
is narrower: confirm whether the private packet is complete enough for branch
review, name missing records, and identify the next clinical owner.

\section*{Use This Before The Main Paper}

\begin{enumerate}
  \item Read this handoff first.
  \item Review original medical records privately; do not put raw records in
  the public repository.
  \item Mark each packet domain below as ready, missing, or not applicable.
  \item If the packet is complete enough, answer the one branch-scope question.
  \item Treat the longer Nakafa Lab main paper as an appendix only if the
  clinician asks for the broader evidence map.
\end{enumerate}

\section*{Current Public State}

Current public-safe handoff label:
\texttt{branch\_review\_handoff\_packet\_incomplete}.

\medskip

\noindent This means the public repo cannot yet ask for a branch decision. The
first useful clinical answer is which packet domains are missing and who owns
them.

\section*{Six Packet Domains To Confirm}

\begin{tabularx}{\textwidth}{@{}p{0.26\textwidth}Y@{}}
\toprule
Domain & What needs private clinical validation \\
\midrule
Diagnosis, genotype, phenotype & Diagnosis category, molecular subtype, and
whether HbF/HPFH or alpha-globin context changes interpretation. \\
Transfusion burden and response & Dates, volume, body weight, product type,
pre-transfusion Hb, Hb increment, interval, and annualized burden. \\
Blood-bank and immune history & Antibody screen, DAT/direct Coombs context,
red-cell phenotype/genotype, matching policy, reactions, spleen context, and
hemolysis workup. \\
Iron, organ-risk, chelation status & Ferritin trend, liver iron MRI, cardiac
\texttt{T2*}, chelator identity, toxicity monitoring, and organ-risk notes. \\
HCT/gene-cell access context & HLA/donor context, transplant or gene-cell
center access, payer path, geography, travel constraints, and fertility
counseling status. \\
Consent, ethics, owner review & Family consent boundaries, private-record
handling, and the qualified owner for each branch question. \\
\bottomrule
\end{tabularx}

\section*{One Branch-Scope Question}

Only after the packet is complete enough for review, please answer:

\begin{quote}
Are any domains still missing before you can answer whether Case-001 belongs
in allogeneic HCT discussion, autologous gene-cell therapy discussion,
non-curative disease modification, standard-care stabilization first, or
benchmark-only tracking?
\end{quote}

\section*{Answer Format Requested}

\begin{enumerate}
  \item Packet state: complete enough, incomplete, or cannot assess.
  \item Missing domains and first records the family should request.
  \item Branch-scope label if answerable: allogeneic HCT discussion,
  autologous gene-cell therapy discussion, non-curative disease modification,
  standard-care stabilization first, benchmark-only tracking, or cannot answer
  from packet.
  \item Next clinical owner: hematology, transfusion medicine, genetics,
  iron/organ-risk specialist, transplant or gene-cell center, or another
  service.
\end{enumerate}

\section*{Records To Attach Or Request}

\begin{itemize}
  \item Current diagnosis note, current HPLC/electrophoresis, and molecular
  testing if available.
  \item Transfusion dates, body weight, blood volume, product type,
  pre-transfusion Hb, post-transfusion Hb if available, interval, and
  reactions.
  \item ABO/Rh/Kell, extended matching policy, antibody screen, named
  antibodies, DAT/direct Coombs with IgG/C3 specificity if available,
  crossmatch problems, and hemolysis workup.
  \item Ferritin trend, liver iron concentration MRI, cardiac \texttt{T2*},
  chelator name, dose, schedule, adherence, side effects, and monitoring.
  \item HLA/donor context, prior referral or rejection, access barriers,
  fertility counseling, and any advanced-therapy or trial discussion.
\end{itemize}

\section*{Boundary}

Do not change transfusion, chelation, immune medicines, supplements, diet,
referral plan, or trial enrollment based on this handoff. Clinical decisions
belong to licensed clinicians. After a doctor replies, map the response into
public-safe labels before writing any public case update.

\section*{Source Anchors}

This handoff follows the July 2 branch-review clinician brief gate, TIF 2025
transfusion, iron-overload, HCT, and gene-manipulation chapters, current
PubMed 2025--2026 gene-cell and HCT benchmarks, and the Nakafa Lab rule that
Quran anchors support verification and expert routing only, not biomedical
claims.

\end{document}
